From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-09 Pi+/paper/finite.tex
Add text in section 4.3
Fixes #114

\begin{definition}
  Here we'll define a type family $FT n$ to be a free group generated by a type $T n$ with the following constructors
  \begin{align*}
     & cancel : i : \Fin[\suc[n]] \to T                                         \\
     & swap : (i : \Fin[\suc[n]]) \to (j : \Fin[\suc[n]]) \to (i + 1 < j) \to T \\
     & braid : (i : \Fin[n]) \to T                                              \\
  \end{align*}
\end{definition}

\begin{definition}[Adjacent transposition]
  \begin{align*}
    transpose : (n : \Nat) \to (k : \Fin[\suc[n]]) \to \Aut[\Fin[\suc[n]]]
  \end{align*}
  by double induction on $n$ and $k$, where
  \begin{align*}
    transpose (n) (0)             & = \lambda
    0 \to 1;
    1 \to 0;
    m \to m
    \\
    transpose (\suc[n]) (\suc[k]) & = \lambda
    0 \to 0;
    S m \to S ((transpose (n)(k)) m)
  \end{align*}
\end{definition}

\begin{proposition}
  $FR$ is a presentation of the symmetrc group, with $f$ and $g$ as follows:
  \begin{align*}
    f (inr (cancel (i))) & = inr (i :: i :: [])                     \\
    f (inl (cancel (i))) & = inl (i :: i :: [])                     \\
    f (inr (swap (i,j))) & = i :: j :: i :: j :: []                 \\
    f (braid (i))        & = i :: S i :: i :: S i :: i :: S i :: []
  \end{align*}
  and
  \begin{align*}
    g (inl (\_)) & = inl ([]) \\
    g (inr (\_)) & = inr ([])
  \end{align*}
\end{proposition}

We now introduce a presentation of the symmetric group $\Sn$.

>>>>

\subsubsection{Coxeter Relations}

We define a binary relation on $\List(\Fin[n])$.

\begin{definition}[Coxeter relation]
  \begin{align*}
    & \mathsf{cancel} : (n \cons n \cons \nil) \cx \nil \\
    & \mathsf{swap} : (\suc[k] < n) \to (n \cons k \cons \nil) \cx (k \cons n \cons \nil) \\
    & \mathsf{braid} : (\suc[n] \cons k \cons \suc[n] \cons \nil) \cx (n \cons \suc[k] \cons n \cons \nil)
  \end{align*}
\end{definition}

The type $\Sn$ is defined as the set-quotient of $\List(\Fin[n])$ by the congruence closure of $\cx$.

\begin{definition}[$\Sn$]
  \(\Sn \defeq \quot{\List(\Fin[n])}{\cx^{\ast}}\)
\end{definition}

\begin{proposition}
  There is a group structure on $\Sn$, where the identity element is $\nil$, multiplication is given by list append, and
  inverse is given by list reversal.
\end{proposition}

\begin{proposition}
  $\Sn$ is equivalent to the generated group given by the normal closure of $\cx$ extended to $\List(\Fin[n] + \Fin[n])$
  along the codiagonal map $[\term{id},\term{id}] : A + A \to A$.
\end{proposition}

We will now show how to generate a Lehmer code from a word in $\Sn$ and back.

\todo{immersion}
